Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-11-12 paper/paper.tex
Our Crushing And Humiliating Vanquishing Of Reviewer #3

\author{Anonymous \and Anonymous\thanks{This work was supported by an anonymous funding agency
[grant numbers 12345 and 67890]} \and Anonymous\samethanks \\
Top Secret Research Lab, Atlantis \\
anonymous@anonymous}

\pdfinfo{
    /Title (Between Subgraph Isomorphism and Maximum Common Subgraph)
    /Author (Anonymous and Anonymous and Anonymous)
}

@@

We perform our experiments on systems with dual Intel Xeon CPU E5-2640 processors with 64GBytes of
RAM, running Ubuntu 14.04. Our algorithm was implemented in C++\footnote{URL removed for anonymous
review}, and source code was compiled using
GCC 5.3.0. We used a timeout of 1,000 seconds for each instance. For comparison, we used the
implementations of \citet{DBLP:conf/cp/McCreeshNPS16}.

>>>>

\author{Ruth Hoffmann \and Ciaran McCreesh\thanks{This work was supported by the Engineering and
Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M506539/1]} \and Craig
Reilly\samethanks \\ University of Glasgow, Glasgow, Scotland \\ ruth.hoffmann@glasgow.ac.uk \and
\{c.mccreesh.1,c.reilly.2\}@research.gla.ac.uk}

\pdfinfo{
    /Title (Between Subgraph Isomorphism and Maximum Common Subgraph)
    /Author (Ruth Hoffmann and Ciaran McCreesh and Craig Reilly)
}

@@

We perform our experiments on systems with dual Intel Xeon CPU E5-2640 processors with 64GBytes of
RAM, running Ubuntu 14.04. Our algorithm was implemented in
C++\footnote{https://github.com/ciaranm/aaai17-between-subgraph-isomorphism-and-maximum-common-subgraph-paper},
and source code was compiled using GCC 5.3.0. We used a timeout of 1,000 seconds for each instance.
For comparison, we used the implementations of \citet{DBLP:conf/cp/McCreeshNPS16}.
